---
title: "Your title here"
author: "Group XX: Albert Y. Kim and P.K. Subban"
date: "November 30th, 2018"
output:
  html_document:
    highlight: tango
    theme: cosmo
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    df_print: kable
---

Read the following bullet points first and then delete them before submitting your work:

* See on Line 8 above we set the theme? You can personalize the HTML 
output theme! See the following [gallery](http://www.datadreaming.org/post/r-markdown-theme-gallery/).
* For R Markdown formatting tips, look at RStudio Menu Bar -> Help ->
    + Markdown Quick Reference Guide
    + Cheatsheets -> R Markdown Cheat Sheet
* The code chunk/block below sets the R Markdown chunk defaults. In other words, if you don't override a subsequent R Markdown code chunk/block's particular options, the following defaults apply. See the first code chunk in "Subsection" for an example of overriding the defaults.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Set R Markdown chunk defaults:
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE, 
  fig.width = 16/2, fig.height = 9/2
)
```


```{r}
# Load all necessary packages here. It's a good idea to load all packages at 
# the beginning of a Rmd file so that collaborators can see in one shot all
# packages they'll need to ensure are installed beforehand:
library(tidyverse)


# Do your data loading and wrangling (if any) here:

```


# Section 1

Hello world

## Subsection 1.1

```{r, echo = TRUE}

```

# Section 2

## Subsection 2.1

```{r}

```

## Subsection 2.2





# References and Citations

* [For Big-Data Scientists, ‘Janitor Work’ Is Key Hurdle to Insights](https://www.nytimes.com/2014/08/18/technology/for-big-data-scientists-hurdle-to-insights-is-janitor-work.html){target="_blank"}, New York Times, August 17 2014.